PropOcData2

### 2021-08-14 R/PropOc Data 3D.Rmd
code for plotting missing data

countDataClean2<-rawPropOcDataClean %>% group_by(SampleCode, source, Distance) %>% summarize(count = n()) %>% filter(count<1000) %>%ungroup() %>% group_by(SampleCode) %>% summarise(MisingTotal = n()*1000-sum(count),TotalMedian = median(count), Mean = mean(count)) %>% mutate(MissingPercent = (1000-Mean)/1000)
#it got a little better, but not that much...
#####
#What are the observations missing?
#####
countDistancesALL<-rawPropOcDataClean %>% group_by(SampleCode,Condition, Distance) %>% summarise(count = n()) %>% ungroup() %>%group_by(Condition) %>%  mutate(difference = max(count)- count)
countDistancesBadOnly<- countDistancesALL%>% filter(difference>0) %>% group_by(SampleCode) %>% summarise(missingDistantes = n()) %>% filter(missingDistantes == 30)
countDistancesGoodOnly<- countDistancesALL%>% filter(difference==0) %>% group_by(SampleCode) %>% summarise(missingDistantes = 30-n()) %>% filter (missingDistantes==0)

leftover<-anti_join(countDistancesALL,countDistancesBadOnly, by = "SampleCode")
leftover<-anti_join(leftover,countDistancesGoodOnly, by = "SampleCode")

#####
#How much of it is outside the ideal boundaries?
#####
CheckBenchmark<-function(benchmark){
CheckPropOc<-rawPropOcDataClean %>% filter(PropOc>benchmark|PropOc<0)
percentInbound<-length(CheckPropOc$SampleCode)/length(rawPropOcDataClean$SampleCode)*100
return(percentInbound)}

CheckBenchmark(1.05)
#the data outside the range should be primarily at really short distances, since this is where the calculation of voxels in the surrounding and sphere of potentially ocuppied space is the largest  
#I think 1.05 is a good benchmark to observe this trend:
CheckPropOc<-rawPropOcDataClean %>% filter(PropOc>1.05|PropOc<0)

>>>>

countDataClean2<-rawPropOcDataClean %>% group_by(SampleCode, source, Distance) %>% summarize(count = n()) %>% filter(count<1000) %>%ungroup() %>% group_by(SampleCode) %>% summarise(MisingTotal = n()*1000-sum(count),TotalMedian = median(count), Mean = mean(count)) %>% mutate(MissingPercent = (1000-Mean)/1000)
#it got a little better, but not that much...
#####
#What are the observations missing?
#####
countDistancesALL<-rawPropOcDataClean %>% group_by(SampleCode,Condition, source,Distance) %>% summarise(count = n()) %>% ungroup() %>%group_by(Condition) %>%  mutate(difference = max(count)- count)

countDistancesALLwt<- countDistancesALL %>% filter(Condition=="wt")
countDistancesALLpqsL<- countDistancesALL %>% filter(Condition=="pqsL")

ggplot()+
  geom_point(data = countDistancesALLpqsL,aes(x=Distance,y=difference, shape = source, color = SampleCode),size=4)+
  labs(title ="Prop Oc Analysis Sampling missing by Source and Distance(Original Run")+
  facet_grid(.~source)+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))
#####
#How much of it is outside the ideal boundaries?
#####
CheckBenchmark<-function(benchmark){
#CheckPropOc<-rawPropOcDataClean %>% filter(PropOc>benchmark|PropOc<0)
CheckPropOc<-rawPropOcData %>% filter(PropOc<0)
percentInbound<-length(CheckPropOc$SampleCode)/length(rawPropOcDataClean$SampleCode)*100
return(percentInbound)}

CheckBenchmark(1.05)
CheckBenchmark(1.1)
CheckBenchmark(1.2)

#the data outside the range should be primarily at really short distances, since this is where the calculation of voxels in the surrounding and sphere of potentially ocuppied space is the largest  
#I think 1.05 is a good benchmark to observe this trend:
CheckPropOc<-rawPropOcDataClean %>% filter(PropOc>1.05|PropOc<0)
